\begin{center}
\section*{PUBLICATIONS}
\end{center}
\addcontentsline{toc}{section}{PUBLICATIONS}

\begin{enumerate}

\item Umar Afzaal, Abdus Sami Hassan, Muhammad Usman and Jeong A. Lee. "On the Evolutionary Synthesis of Fault-resilient Arithmetic Circuits". IEEE Transactions on Evolutionary Computation. (2021) (Under review at the time of thesis submission)

\item Umar Afzaal, Abdus Sami Hassan, and Jeong-A. Lee. "Improved error detection performance of logic implication checking in FPGA circuits." Microprocessors and Microsystems 78 (2020): 103179.

\item Umar Afzaal, and Jeong-A. Lee. "Trading the Reliability of Approximate TMR in FPGAs with the Cost of Mitigation." 2020 23rd Euromicro Conference on Digital System Design (DSD). IEEE, 2020.

\item Abdus Sami Hassan, Umar Afzaal, Tooba Arifeen, and Jeong A. Lee. "Input-Aware Implication Selection Scheme Utilizing ATPG for Efficient Concurrent Error Detection." MDPI Electronics 7, no. 10 (2018): 258.

\item Inayat Ullah, Zahid Ullah, Umar Afzaal, and Jeong-A. Lee. "DURE: An energy-and resource-efficient TCAM architecture for FPGAs with dynamic updates." IEEE Transactions on Very Large Scale Integration (VLSI) Systems 27, no. 6 (2019): 1298-1307.


\item Umar Afzaal, and Jeong-A. Lee. "Low-cost Hardware Redundancy for Fault-mitigation in Power constrained IoT Systems." 2020 International Conference on Information and Communication Technology Convergence (ICTC). IEEE, 2020.

\end{enumerate}




\pagebreak  % <----- this pagebreak is required here


